Response to Reviewers - Article 4780

### 2023-06-26 review/B-response.Rmd
update response

**\textcolor{purple}{The data historical\_tmax contains daily weather station data for the two periods: 1971-1975 and 2016-2020 and amounts to 3.2MB, which is not suitable to include in the package given its size. The tmax\_hist data, which was included in the package, is now removed, given its similarity to the climate\_aus data, which is more useful. The scripts to generate historical\_tmax are provided with the paper.}**

>>>>

**\textcolor{purple}{The data historical\_tmax used in the paper now replaces the tmax\_hist data in the package.}**
